working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-03-05 Manuscript_draft/Manuscript_draft.Rmd
edits

\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=3,fig.width=6,fig.cap="Average effect size and confidence intervals (95%) of the 9 heterospecific treatments of 50% pollen to the different 10 focal species coloured by family."}

>>>>

\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=2.5,fig.width=6,fig.cap="Average effect size and confidence intervals (95%) of the 9 heterospecific treatments of 50% pollen to the different 10 focal species coloured by family."}
